\section{Continuous functionals. Hahn-Banach theorem}
$X$ --- linear set, $f \colon X \to \R$ --- linear functional if $f(\alpha x_1 +
\beta x_2) = \alpha f(x_1) + \beta f(x_2)$ \\
Let $X$ be arbitrary normed space. We call functional $f$ continuous on $X$ if
$x_n \to x \implies f(x_n) \to f(x)$. Because in normed space addition and
scalar multiplication are continuous, by functional lineriarity $f(x_n) - f(x) =
f(x_n - x),\ x_n \to x \iff x_n - x \to 0,\ f(0) = 0$\\

\begin{stm}
  $f$ is continuous on $X$ if and only if $f$ is continuous in 0.
\end{stm}

\begin{defn}
  $\sup\limits_{\|x\| \leq 1}{|f(x)|} = \|f\|$, $f$ --- limited $\iff \|f\| < +\infty$
\end{defn}

\begin{thm}
  Linear functional is continuous if and only if it is limited.
\end{thm}

\begin{proof}
  Let $f$ be limited linear functional:
  \begin{align*}
    &\|f\| < +\infty,\ |f(x)| \leq 
      \|f\| \cdot \|x\|,\ x_n \to 0 \implies \|x_n\| \to 0 \\
    &|f(x_n)| \leq \tendsto{\|f\| \cdot \|x_n\|}{0} \implies f(x_n) \to 0
  \end{align*}
 Let $f$ be continuous functional: 
 \begin{align*}
   &\|f\| = +\infty = \sup\limits_{\|x\| \leq
     1}|f(x)|,\ \forall b \in \N : \exists x_n : \|x_n\| \leq 1,\ |f(x_n)| > b \\
   &\abs{f(\dfrac{x_n}{n})} > 1,\ \norm{\dfrac{x_n}{n}} = \dfrac{\|x_n\|}{n} \leq
     \dfrac{1}{n}\ \dfrac{x_n}{n} \to 0 \implies f(\dfrac{x_n}{n}) \to 0 \contr \qedhere
 \end{align*}

\end{proof}

\begin{note}
  By functional lineriarity it's kernel is linear set.
\end{note}

\begin{thm}
  Functional $f$ is continuous if and only if $\ker{f}$ is closed in $X$.
\end{thm}

\begin{proof}
  Let $f$ be continuous, then 
  \[
    x_n \in \ker{f},\ x_n \to x \implies
    \tendsto{f(x_n)}{0} \to f(x) \implies f(x) = 0 \implies x \in \ker{f}
  \]
  Let $\ker{f}$ be closed, $\codim{(\ker{f})} = 1$
  \begin{align*}
    &\exists e \in X : \forall x = y + t \cdot e,\ y \in \ker{f},\ t \in \R \\
    &f(x) = f(y) + t \cdot f(e) = t \cdot f(e) \\
    &x_n = y_n + t_n \cdot e \to x = y + t \cdot e,\ f(x_n) = t_n \cdot f(e)\\
    &?t_n \to t \implies t_n \cdot f(e) \to t \cdot f(e) = f(x) \implies f(x_n) \to
      f(x). \\
    &x_n = y_n + t_n \cdot e,\ x = y + t \cdot e,\ x_n \to x,\ y_n,y \in \ker{f}.
  \end{align*}
  If we can prove that all converging subsequences $t_{n_k} \to t^*$ then $t_n$ will
  converge too. 
  \begin{align*}
    &y_{n_k} = x_{n_k} - t_{n_k} \cdot e \\
    &y_{n_k} \in \ker{f} \to x - t^* \cdot e \implies z = x - t^*
      \cdot e \in \ker{f} \\
    &x = z + t^* \cdot e,\ x = y + t \cdot e \implies t^* = t. \qedhere
  \end{align*}
\end{proof}

\noindent
$X$ --- normed space, $Y$ --- linear set in $X$, $Y$ dense in $X$.
$C[0, 1]$ \\
$\forall \epsilon > 0\ \exists P_n(x) : |f(x) - P_n(x)| < \epsilon\ \forall x \in [0, 1]$\\ 
S.N. Bernstein constructively showed these polynoms. \\
$B_n(f, x) = \sum\limits_{k = 0}^n C_n^k f(\dfrac{k}{n}) x^k (1 - x)^{n - k}$ \\
From functional analysis point of view Weierstrass theorem means that:
\[
  Y = \{\text{all}\ P_n(x)\}\ \text{--- linear set in}\ C[0, 1]
\]
That means $Y$ is dense in $C[0, 1]$.

\begin{note}
  Let $f_0$ be continuous, linear functional on $Y$. $\exists ?$ continuous,
  linear functional $f$ on $X : f|_Y = f_0$
\end{note}

\begin{thm}
  Given task is always has (unique) solution.
\end{thm}

\begin{proof}
  $f$ --- continuous on $X$, $g$ --- continuous on $X$, $f|_Y = g|_y$
  \begin{align*}
    &\forall x \in X,\ \cl{Y} = X\ \exists y_n \in Y : y_n \to x \\
    &f(y_n) \to f(x),\ g(y_n) \to g(x) \implies f(x) = g(x)
  \end{align*}
\end{proof}

