\section{Kolmogorov theorem}
\begin{defn}
  $X$ --- linear set, $\tau$ --- topology on $X$, $\alpha x$, $x + y$ are
  continuous on $\tau$.

  \noindent $E(x) \subset X$ is called a neighbourhood of $x \in X$ if there
  exists open set $U \in \tau: x \in U \subset E(x)$.
  
  \noindent $(X, \tau)$ is called a \textbf{topological vector space}.
  
  \noindent $\alpha x$ continuity means:
  \[
    \forall E(\alpha_0 x_0)\ \exists \delta > 0,\ \exists E(x_0) \colon
    |\alpha - \alpha_0| < \delta,\ x \in E(x_0) \implies
    \alpha x \in E(\alpha_0 x_0),
  \]
  or
  \[
    \alpha_0 x_0 = \lim_{\substack{\alpha \to \alpha _0\\ x \to x_0}} \alpha x.
  \]
  \noindent $x + y$ continuity means:
  \[
    \forall E(x_0 + y_0)\ \exists E(x_0), E(y_0) \colon
    x \in E(x_0), y \in E(y_0) \implies x + y \in E(x_0 + y_0),
  \]
  or 
  \[
    x_0 + y_0 = \lim_{\substack{x \to x_0\\ y \to y_0}}(x + y).
  \]
\end{defn}

\noindent
It is clear that normed and countably-normed spaces are just special cases of
topological vector space.

\noindent
Let's fix $x_0$.\\
It is clear that $f(x) = x + x_0$ is a bijection $X \to X$ \\
$f^{-1}(y) = y - x_0$ \\

\begin{defn}
  A function $f \colon X \to Y$ between two topological spaces $(X, \tau_X)$ and
  $(Y, \tau_Y)$ is called a \textbf{homeomorphism} if it has the following properties:
  \begin{enumerate}
  \item $f$ is a bijection
  \item $f$ is continuous 
  \item the inverse function $f^{-1}$ is continuous
  \end{enumerate}
\end{defn}

\noindent
If $G$ is open in $X$, $G \in \tau$, then $x_0 + G = \Set{x_0 + x, x \in G}$ is
open too. \\
This means any topology is invariant relative to shift. \\

\begin{defn}
  A \textbf{neighbourhood basis} or \textbf{local basis} for a point $x$ is a 
  \[
    \mathcal{B}(x) \subset \mathcal{V}(x) 
  \]
  such that 
  \[
    \forall V \in \mathcal{V}(x) \quad \exists B \in \mathcal{B}(x): B \subset V.
  \]
  Where $\mathcal{V}(x)$ is the collection of all neighbourhoods for the point
  x.
  We will use $\Sigma$ to denote neighbourhood basis for point 0.
\end{defn}

$x \to 0$ in $\tau$ $x + x \to 0 + 0 = 0$\\
$\forall V \in \sigma\ \exists U \in \sigma \colon U + U \subset V,\ 2 \cdot U
\subset U + U \subset V$ \\
$\lambda x \to 0,\ \lambda \to 0,\ x \to 0\ \forall V \sigma\ \exists \epsilon >
0,\ U \in \sigma\ |\lambda| \leq \epsilon \implies \lambda U \subset V$ \\
$\bigcup\limits_{|\lambda| \leq \epsilon} \lambda U$ --- radial, also zero
neighbourhood. That means if $X$ is a topological vector space then system of open
sets is shift-invariant and such base can be created that:
$\sigma$ 
\begin{enumerate}
\item $\forall V \in \sigma\ \exists U \in \sigma: U + U \subset V$
\item All elements of $\sigma$ are radial, circled sets.
\end{enumerate}

\begin{defn}
  Topological space is called Hausdorff space, if any pair of points can be
  divided by their neighbourhoods, i.e. there exist disjoint neighbourhoods of such points.
\end{defn}

\begin{thm}[Kolmogorov]
  Hausdorff topological vector space is normalizable if and only if zero has at least one 
  bounded, convex neighbourhood (the set is bounded if it is absorbed by any zero's neighbourhood).
\end{thm}

\begin{proof}
  Minkowski functional is seminorm if and only if it is produced by radial,
  circled set. If space is normalizable then unit ball is bounded, convex zero's
  neighbourhood.
  By the former characterization of vector space topology, having bounded, convex zero's
  neighbourhood we can assume we have radial, circled neighbourhood. Produce Minkowski
  functional using it (it will be seminorm). We can assume the set is bounded.
  $V$ --- bounded, convex, circled. $\Set{\dfrac{1}{n}V, b \in \N}$
  $\forall$ bounded.
  $W$ $|\lambda| \geq \lambda_0$, $V \subset \lambda W$
  $\exists n_0 \in \N > \lambda_0$
  $V \subset n_0 W$ $\dfrac{1}{n_0} V \subset W$ \\
  Now we only have to check that functional is norm.
  $p_V(x) = 0 \implies x = 0?$ \\
  $x \in \bigcap\limits_{n = 1}^\infty \left(\dfrac{1}{n} V\right) = \{0\}$
\end{proof}

\begin{ex}
  $\R^\infty = \Set{(x_1, \dotsc, x_n, \dotsc)}$ \\
  $\Set{\bar{x} \colon x_{i_1} \in (-\delta_1, \delta_1),\ x_{i_2} \in
    (-\delta_2, \delta_2), \dotsc, x_{i_p} \in (-\delta_p, \delta_p),\ \delta_j
    > 0}$ --- this system will produce zero's base and insure coordinatewise
  convergence. $P_n(\bar{x}) = |x_n|$ all of the seminorms are essential, which
  means the space is not normalizable.
\end{ex}
